Polyester RNA-seq simulation study

### 2018-08-02 datasets/RNA-Seq/polyester-simulation.Rmd
Factor model matrix for polyester; polyester assumes effect sizes are log fold changes

  # things needed to simulate with Polyester
  groupPolyester = rep(c(-1,1),each=sampleSize)
  modPolyester = model.matrix(~-1 + groupPolyester)

@@

    # randomly sample a log2FC from N(0,1) 
    log2FC[DE] <- rnorm(nDE, sd = 1)
    dat_alt[DE,] = create_read_numbers(mu[DE], paramPolyester$fit, p0[DE], 
                                  n=sampleSize*2, beta=cbind(log2FC[DE]/2), 
                                  mod=modPolyester)
  }

>>>>

  # things needed to simulate with Polyester
  groupPolyester = rep(c(0,1),each=sampleSize)
  modPolyester = model.matrix(~-1 + groupPolyester)

@@

    # randomly sample a log2FC from N(0,1) 
    log2FC[DE] <- rnorm(nDE, sd = 1)
    # polyester assumes FC is on the log scale
    dat_alt[DE,] = create_read_numbers(mu[DE], paramPolyester$fit, p0[DE], 
                                  n=sampleSize*2, beta=cbind(log(2^log2FC[DE])), 
                                  mod=modPolyester)
  }
